%-------------------------
% Resume in Latex - Dense SWE/AI Version
% Font: Charter - 10pt for high density
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}
\usepackage{charter} 

\input{glyphtounicode}

% Tight Margin setup for dense look
\geometry{left=1.0cm, top=1.0cm, right=1.0cm, bottom=1.0cm}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Standardized Section Formatting - Compressed
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% ATS Parsing
\pdfgentounicode=1

% Custom Commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1.8pt}}
  }
}

\newcommand{\resumeEntryHeading}[3]{
  \vspace{2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \textit{#2} & \small #3 \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeEducationEntry}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #3 \\
      \textit{\small #2} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small\textbf{#1} & \small #2 \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{
  \begin{itemize}[leftmargin=0.15in, label={}, topsep=2pt, partopsep=0pt, itemsep=4pt, parsep=0pt]
}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=2pt, partopsep=0pt, itemsep=1.5pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\renewcommand\labelitemi{$\bullet$}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \textbf{Yashvi Bansal}} \\ \vspace{4pt}
    \small 
    +91 62831 62131 $|$
    \href{mailto:bansaly0203@gmail.com}{\underline{bansaly0203@gmail.com}} $|$ 
    \href{https://linkedin.com/in/yb0203}{\underline{linkedin.com/in/yb0203}} $|$ 
    \href{https://github.com/yb0203}{\underline{github.com/yb0203}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\vspace{2pt}
\small{Software Engineer with 2+ years of experience delivering scalable banking automation and AI-powered solutions. Specialized in \textbf{LLM engineering, RAG architecture}, and platform automation. Passionate about applying AI and software engineering to solve complex problems and create measurable business impact.}

%-----------SKILLS-----------
\section{Skills}
\vspace{2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks}{: Java, Python, Flask, SQL, C++, HTML, CSS, PostgreSQL, C} \\
     \textbf{AI \& LLMs}{: LangChain, Vector databases, OpenAI, RAG Architecture, DeepEval, Ollama, Prompt Engineering, Hugging Face, Multi-Agent Framework, AI guardrails} \\
     \textbf{Core CS}{: Microservices Architecture, RESTful API Design, Distributed Systems, Multithreading, Data Structures \& Algorithms, Object-Oriented Programming (OOP), System Design, Agile/Scrum} \\
     \textbf{Certifications}{: Hugging Face -- AI Agents; SOLID Principles \& Design Patterns (Java); Design Thinking}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeEntryHeading{Software Development Engineer - 1}{Kotak Mahindra Bank Limited}{Aug 2023 -- Present}
  \vspace{2pt}
  \textbf{Automation Infrastructure}
  \resumeItemListStart
    \resumeItem{Constructed a \textbf{Java-based API automation framework} for Finacle APIs, embedding core banking business logic end-to-end. Reduced testing time by \textbf{90\%} by encoding domain-specific workflows into reusable automation scripts.}
    \resumeItem{Designed a \textbf{Gherkin-based BDD framework} translating banking business requirements into executable test scenarios within hours, enabling faster validation of critical financial workflows.}
    \resumeItem{Engineered \textbf{automated test data generation}, eliminating manual preparation and accelerating QA cycle times significantly. Reduced manual data prep by \textbf{70\%}, enabling test suites to execute faster across all banking modules.}
    \resumeItem{Developed a \textbf{reusable parameterized CI template stage} for integration testing, deployable across all engineering pipelines. Empowered teams to selectively configure pipeline stages and jobs, standardizing test infrastructure across \textbf{5+ engineering teams} organization-wide.}
  \resumeItemListEnd
  \vspace{2pt}
  \textbf{Centralized Reporting Platforms}
  \resumeItemListStart
    \resumeItem{Spearheaded a \textbf{centralized report server} using \textbf{Python and Flask}, automating onboarding for teams across the organization seamlessly. Boosted cross-team visibility and slashed report retrieval time by \textbf{80\%}.}
    \resumeItem{Pioneered an \textbf{AI-driven bug triage engine} that classifies errors and ranks them by priority automatically. Delivered \textbf{automated root cause analysis} with confidence scores, cutting mean time to resolution significantly.}
    \resumeItem{Enforced \textbf{clean code practices} and modular architecture, improving maintainability and scalability of the report server codebase, streamlining future enhancements and reducing technical debt.}
  \resumeItemListEnd
  \vspace{2pt}
  \textbf{AI Security Engineering}
  \resumeItemListStart
    \resumeItem{Developed an \textbf{LLM evaluation framework} identifying \textbf{8+ OWASP security vulnerabilities} across internal banking AI agents. Successfully detected critical risks including \textbf{Prompt Injection} and \textbf{Sensitive Data Disclosure}, preventing exposure prior to production.}
    \resumeItem{Integrated banking business requirements into \textbf{DeepEval} by building custom modular classes tailored to domain-specific evaluation scenarios. Enabled systematic validation of \textbf{LLM responses} against banking metrics, ensuring accuracy and compliance across deployments.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{GitaBae - AI Wisdom Chatbot} $|$ \textit{Python, LangChain, Pinecone, OpenAI, Streamlit}}{Jan 2024}
  \resumeItemListStart
    \resumeItem{Built \textbf{RAG} pipeline using \textbf{LangChain} and \textbf{Pinecone Vector DB} to retrieve and serve contextually relevant responses from religious Gita verses, with \textbf{OpenAI} embeddings and multi-turn conversation memory.}
    \resumeItem{Engineered content moderation middleware with \textbf{semantic similarity search}, topic filtering, and crisis detection, automatically routing sensitive queries to human support with \textbf{prompt injection} protection.}
  \resumeItemListEnd
  \resumeProjectHeading{\textbf{Vibe Check - AI-Powered MCP Server} $|$ \textit{Node.js, Model Context Protocol, Git API}}{Nov 2023}
  \resumeItemListStart
    \resumeItem{Architected a \textbf{Node.js MCP server} abstracting \textbf{Git CLI workflows} into natural language interfaces, empowering non-technical contributors to execute rebases, merges, and cherry-picks via plain English.}
    \resumeItem{Engineered \textbf{LLM prompt chains} to parse Git diffs and generate structured, standardized release notes. Leveraged \textbf{OpenAI function calling} with multi-step chaining, achieving \textbf{95\% intent-parsing accuracy} across diverse inputs.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeEducationEntry
    {Indian Institute of Technology, Banaras Hindu University (IIT-BHU)}
    {Bachelor of Technology \textnormal{--} CGPA: 8.69 / 10}
    {Jul 2019 -- May 2023}
    {Varanasi, UP, India}
\resumeSubHeadingListEnd


\end{document}
